State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-24 prism-backend/research/soa_review/ac.tex
Some synthesis effort in the AC part.

First proposed in \cite{chau85}.
CL signatures (idemix) \cite{cl01,cl04}.
UC formalisation in \cite{cdhk15}.
Brands works (U-prove).
Coconut paper, referenced in \cite[Section 1]{cdl+20}: anonymous credentials with
threshold opening.

@@

Anonymous Credentials (ACs) were first proposed by Chaum \cite{chau85}, and
later formally treated and optimized in a series of papers by Camenisch and
Lysyanskaya \cite{cl01,cl02,cl04}. Roughly speaking, users receive credentials
from an issuing organization, which can then use to authenticate against some
verifier. The main property is that this authentication process can be done
in a privacy-preserving way. This typically means that the verifier cannot
link different authentication processes by that same user. And, usually, in
credentials composed by multiple attributes, that the verifier only learns
the attributes that the user is willing to share (or a function of them).

@@

\paragraph{Main approaches.} %

@@

@@

\begin{itemize}
\item : Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures. \cite{kkl+16} achieves similar results with a
  different approach?
\end{itemize}

>>>>

\todo{Big: Brands's line of works (U-prove).}

@@

Anonymous Credentials (ACs) were first proposed by Chaum \cite{chau85}, and
further studied, formally treated, and optimized, in a series of papers by
Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} and, independently, by Brands
\needcite\footnote{Camenisch and Lysyanskaya line of work is well known for
  IBM's Idemix system, and Brands's work for Microsoft's U-Prove. More detail
  appears in the sequel.}. In an AC system, roughly speaking, users receive
credentials from an issuing organization, which they can then use to
authenticate against some verifier. The main property is that this
authentication process can be done in a privacy-preserving way. This typically
means that the verifier cannot link different authentication processes by that
same user. Usually, credentials are composed by multiple attributes, such that
the verifier only learns the attributes that the user is willing to share (or a
function of them).

@@

\paragraph{Main approaches.} %
The more fruitful line of work within the AC domain is the one initiated by
Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} (henceforth, CL credentials or,
when referring to the underlying signature schemes defined in \cite{cl02,cl04},
CL signatures). The core idea is simple: in order to build a (basic) AC
system, all that is needed are a commitment scheme, and a signature scheme
with efficient protocols for signing committed values, and proving knowledge
of a signature. From this, a basic AC system can be derived as in \figref{XXX}.
Essentially:

\begin{itemize}
\item User $A$ randomly produces a secret value $s_A$, and commits to it,
  producing $c_A$.
\item User $A$ interacts with issuer $I$ to get a signature on $s_A$. To
  avoid leaking the secret to $I$, $A$ uses $c_A$, proving knowledge of the
  associated secret. The produced signature $\sigma_A$, is $A$'s anonymous
  credential.
\item When $A$ needs to convince a verifier $B$ that she owns a valid credential
  issued by $I$, she just has to create a zero-knowledge proof of knowledge
  of $\sigma_A$.
\end{itemize}

Usually, the commitment to the user's secret key is known as a pseudonym, or
in short form, \emph{nym}. These nyms have proven to be a useful component to
ensure security and privacy properties -- and are also leveraged in many group
signature and DAA works.

A large part of the academic works in the AC domain follow this approach, which
is then extended to support enhanced functionality. For instance, in order to
support multiple issuers (and, in some sense, multiple attributes)
\cite{cl01,cl02,cl04} \todo{check if the references are correct} require an
extra protocol for proving, in zero-knowledge, equality of two committed and signed values.
This allows user $A$, with credential $\sigma_A^I$ obtained from issuer $I$ and
credential $\sigma_A^J$ obtained from issuer $J$, to prove $J$ that she has a
valid credential from $I$, by issuing a zero-knowledge proof of equality for
both credentials. Now, if each credential is associated with a different set of
attributes, this also lets to ``naively'' build multi-attribute AC systems.

For multi-attribute ACs, though, much more efficient variants are possible. To
begin with, CL signatures allow signing blocks of messages (and commitments),
which can be seen as attributes signed by the issuer. BBS+ signatures
\cite{am06,cdl16b}, and PS16 signatures \cite{ps16} also support similar
functionality, and have been leveraged to build multi-attribute AC systems
too (e.g., \cite{cks10} gives a construction with BBS+ credentials, and
\cite{sms+19,halp20} are based on PS16). These family of signatures on blocks
of messages have yet another very useful property: signatures are easily
randomizable, which can be used (along with the previously mentioned
zero-knowledge proofs) to make unlinkable showings of the same credential.
AC systems achieving the latter property of unlinkable showings are said
to offer \emph{multi-show} credentials.

Most of these systems also have in common that, being based on building blocks
leveraging discrete logarithm structures, they are easily extended to prove
arbitrary statements on the credentials attributes -- such as the usual ``Over
18'' claim. However, while it is certainly doable, the approach does not scale
for complex statements involving multiple attributes \todo{some concrete
  figures?}

Restricting the expressiveness, and focusing on letting the credential holder
reveal only a subset of the attributes in a credential, more efficient schemes
have been proposed, leveraging algebraic tricks such as structure-preserving
signatures on equivalence classes (SPS-EQ), along with vector commitment schemes
\cite{cdhk15}, or set commitment schemes \cite{fhs19}. The former uses Lagrange
interpolation to allow revealing only a subset of the committed messages;
\todo{what was the specific technique of \cite{fhs19}?}. \cite{fhs19}, is more
efficient, as avoids complex zero-knowledge proofs; however it does not support
blind issuance of credentials, as opposed to \cite{cdhk15} \todo{confirm this
  last part, and refine}.

\todo{Mention the subline of delegatable credentials, with controlled
  malleability.}

All AC systems mentioned up to this point follow, up to small variations, the
same approach: randomizable signatures on sets of (committed) messages, with
(somehow) efficient proofs. \todo{Move to the ones based on predicate
  encryption.}

\todo{End with the MAC-based approach.}

@@

  \note{The concept of aggregation here is different than the one in \cite{cl11}.
    In the latter, users can aggregate credentials from different issuers. Here,
    this is not possible, as aggregation won't work for different signing keys
    (i.e., issuer keys). Hence, aggregation rather refers to receiving multiple,
    independently signed, attributes by the same issuer, and then combining them
    into a single credential by that same issuer.}

@@

\begin{itemize}
\item \cite{bckl08}.
\item \cite{sand20}.
\item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different approach?
\end{itemize}
